### 2014-01-27 brains-introduction.tex
Change master document meta-data. brains-introduction is now completely clean.
Minor phrasing

% !TEX root = /Users/camille/Shared/Dropbox/BrainCopyPaste/brainscopypaste.tex
% ============================
\section{Introduction} % =====
% ============================

@@

\smallskip
Stepping back, we observe a gap between, on one side, macro-level empirical studies of the diffusion dynamics in a social system and, on the other side, studies focused on micro-level transformations of representations --- these latter studies being either strongly normative, or whose results are difficult to integrate with realistic cultural epidemiology models.

>>>>

% !TEX root = brainscopypaste.tex
% ============================
\section{Introduction} % =====
% ============================

@@

\smallskip
Stepping back, we observe a gap between, on one side, macro-level empirical studies of the diffusion dynamics in a social system and, on the other side, studies focused on micro-level transformations of representations --- these latter studies being either strongly normative, or whose results are difficult to articulate with realistic cultural epidemiology models.
